---
title: ' Breweries & Brew Pubs in the USA'
author: "Vivek Mangipudi"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: no
---


```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Breweries & Brew Pubs in the USA

library(ggplot2)
library(readr)
library(leaflet)
library(knitr)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(plotly)
library(maps)
library(ggmap)
library(gridExtra)

datz <- read_csv("../input/7160_1.csv")
```

```{r,echo = FALSE}
datz %>%
   select(province) %>%
   group_by(province) %>%
   summarize(Total =n()) ->df
dfc<-df

df$hover <- with(df, paste("Total Breweries", `Total`))
# give state boundaries a black border
l <- list(color = toRGB("black"), width = 1)

# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('Blue')
)

```
# Plotting counts by state on a map
```{r,echo = FALSE}

library(plotly)

plot_ly(df, z = df$`Total`, text = df$hover, locations = df$province, type = 'choropleth',
        locationmode = 'USA-states', color = df$`Total`, colors = 'Purples',
        marker = list(line = l), colorbar = list(title = "Number")) %>%
  layout(title = 'Breweries by State<br>(Hover for breakdown)', geo = g)
```
<br>

# Plotting locations on map   (Interactive) 

<p> There are about 1961 missing long-lat pairs </p>
```{r, echo = FALSE}
datz<-na.omit(datz)
leaflet(datz) %>% addTiles('http://{s}.tile.openstreetmap.fr/hot/{z}/{x}/{y}.png', attribution='Map tiles by <a href="http://stamen.com">Stamen Design</a>, <a href="http://creativecommons.org/licenses/by/3.0">CC BY 3.0</a> &mdash; Map data &copy; <a href="http://www.openstreetmap.org/copyright">OpenStreetMap</a>') %>% 
  setView( -95.7129, 37.0902, zoom = 4) %>% 
  addCircles(~long, ~lat, popup=datz$name, weight = 3, radius=40, 
             color="#ffa500", stroke = TRUE, fillOpacity = 0.9) %>% 
  addLegend("bottomleft", colors= "#ffa500", labels="Locations", title="Pubs-Breweries : USA")

```

<br>

<h4> Ordering States by number of Breweries-Pubs </h4>
```{r,echo = FALSE}
dfc<-arrange(dfc,-Total)

kable(dfc)
```
<br> 


<p> Apart from CA in the west coast, it appears that there are more pub-breweries along the east coast</p> 



<h3> NOTE: Possible Inconsistencies in data: </h3>
<p>*1*. One entry is :     
2930 Centre Ave N E,Bottle Return Centers, Brewers, Wholesale Beer Distributors,Calgary,US,us/ab/calgary/2930centreavene,NA,NA,Brewers Distributor Ltd.  
4035311057, T2A, 4Y2,AB, http://www.bdl.ca/ </p>  
<p> This is not in USA, Calgary is in CANADA.</P> <br>
<p>*2* . The column `province` has most entries as State codes, but some are names of cities ex : Sacramento, Los Angeles, LA,San Diego,St. Louis,Tampa etc.   </p>
